\bf Focusing on Fast Neural Network Inference

### 2018-05-16 wnmt.2018/wnmt.tex
small numerical differences

@@

After further experimentation, we decided to use sentence length normalization and NVidia's Tensor Core matrix multiplication which increased translation quality as well as translation speed. The beam was kept at 1 throughout for the fastet possible inference.

@@

Our second system uses multiplicative-LSTM in the encoder and the first layer of a decder, and a GRU in the second layer, using an extension of the Nematus toolkit which supports such model. We trained 2 systems with differing vocabulary sizes and varied the beam sizes before chose the the settings that produces good translation quality on the validation set, Table~\ref{tab:mLSTM BLEU - vocab sizes}.

\begin{table}
\small
\begin{center}
\begin{tabular}{|l|r|r|r|r|r|} \hline
		& \multicolumn{5}{|l|}{\emph{Beam size}}	\\ \hline	
Vocab size	& 1	& 2	& 2	& 4	& 5 \\ \hline
40,000 		& 23.45	& 24.15	& 24.48	& 24.42	& 24.48 \\ 
50,000		& 23.32	& 24.04	& 	&	& \\ \hline
\end{tabular}
\end{center}
\caption{Validation set BLEU for mLSTM-based model}
\label{tab:mLSTM BLEU - vocab sizes}
\end{table}

>>>>

We used a variety of GPUs to train the models but all testing was done on an Nvidia V100. Translation quality was measured using BLEU, specifically multi-bleu as found in the Moses toolkit. The validation and test sets provided by the shared task organisers were used to measure translation quality, but a 50,000 sentence subset of the training data was used to measure translation speed to obtain longer, more accurate measuremenrs.

@@

After further experimentation, we decided to use sentence length normalization and NVidia's Tensor Core matrix multiplication which increased translation quality as well as translation speed. The beam was kept at 1 throughout for the fastest possible inference.

@@

Our second system uses multiplicative-LSTM in the encoder and the first layer of a decder, and a GRU in the second layer, using an extension of the Nematus toolkit which supports such model. We trained 2 systems with differing vocabulary sizes and varied the beam sizes before choosing the the settings that produces good translation quality on the validation set, Table~\ref{tab:mLSTM BLEU - vocab sizes}.

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|} \hline
		& \multicolumn{2}{|l|}{\emph{Vocab size}}	\\ \hline	
Beam size	& 40,000	& 50,000 \\ \hline
1 		& 23.45		& 23.32	\\ 
2		& 24.15		& 24.04	\\
3		& 24.48		&  	\\
4		& 24.42		& 	\\
5		& 24.48		& 	\\ \hline
\end{tabular}
\end{center}
\caption{Validation set BLEU for mLSTM-based model}
\label{tab:mLSTM BLEU - vocab sizes}
\end{table}
